% the sample slide is created with 16:9 aspect ratio
\documentclass[aspectratio=169]{beamer}
%\documentclass{beamer}
\useoutertheme{miniframes}


% remove the options if you do not want to have them
\usetheme[
	background=empty,
	logo=rosslogo
]{UMRoss}

% the background and logo are in the images directory
\graphicspath{{images/}}

% information for the title page
\author{Tae Uk Seo}
\title{Michigan Ross Beamer Theme}
\subtitle{An unofficial theme for Michigan Ross}
\institute{Stephen M. Ross School of Business, University of Michigan}
\date{\today}

\begin{document}
	% use plain option to remove the page number from the title slide
	\begin{frame}[plain]
		\titlepage
	\end{frame}

\section{Introduction}
	
	\begin{frame}{Welcome to Ross!}
	Michigan is a Midwestern state of the United States of America. 
		\begin{itemize}
			\item Residents of Michigan are known as \emph{Michiganders}.
				\begin{itemize}
					\item I am a subitem
				\end{itemize}
			\item Artes, Scientia, Veritas.
			\item \textbf{this is a bold text}
			\item \alert{this is an alert}.
		\end{itemize}
	\end{frame}

	\begin{frame}{Blocks}
		\framesubtitle{This is a subtitle}
		\begin{block}{Standard Block}
			This is a standard block.
		\end{block}
	
	\end{frame}
	
	\begin{frame}{Math}
		Mathematics is the queen of sciences and arithmetic is the queen of mathematics.
		\begin{align*}
			\Pr(Y \geq 120) &= \Pr\left(Y-n\mu \geq 120-n\mu \right)\\
			&= \Pr\left( \frac{Y-n\mu }{\sqrt{n}\sigma} \geq \frac{120-n\mu }{\sqrt{n}\sigma} \right)\\
			&=\Pr\left( Z \geq \frac{120-n\mu }{\sqrt{n}\sigma} \right)\\
			&=\Pr\left( Z \geq \frac{120-100 \cdot 1 }{10 \cdot 1} \right)\\
			&=\Pr\left( Z \geq 2\right)
		\end{align*}
	\end{frame}

	\begin{frame}{Two Columns}
		We can also add two columns in the slides.
		\begin{columns}[t]
			\begin{column}[T]{0.4\textwidth}
				This is the first column. In this column, we can also add a block for instance.
				\vspace{1em}
				\begin{block}{Block}
					I am a block in a column.
				\end{block}
			\end{column}
			\begin{column}[T]{0.4\textwidth}
				\begin{itemize}
					\item In this column,
					\item we just add the
					\item bullet points.
				\end{itemize}
			\end{column}
		\end{columns}
	\end{frame}


\section{Example}

\begin{frame}
\frametitle{Literature}
Fund managers inflate quarter-end NAV by purchasing stocks already in their portfolios.

\begin{itemize}
\item Sias and Starks (1997): tax-loss selling.
\item Carhart et al (2002), Bernhardt and Davies (2005): cite managerial compensation incentives.
\end{itemize}
Existing models of funds have explained this in different ways.

\begin{itemize}
\item Bernhardt and Davis (2009) model fund managers who want to attract investor inflows.
\begin{itemize}
\item Trades have price impact: it is thus optimal to trade securities they already own.
\end{itemize}
\item Dow and Gorton (1997): portfolio pumping arises because uninformed portfolio managers try to mimick the holdings of informed portfolio managers.
\end{itemize}
\end{frame}

\section{Acknowledgements}

\begin{frame}{Acknowledgements}
		The theme is developed on the base of \textsl{Saarland} theme by Kailash Budhathoki. The original version is available at:
		\begin{url}
		https://github.com/kailashbuki/beamerthemesaarland
		\end{url}.
\end{frame}
	
		
		
	
\end{document}
